Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-02 paper.tex
Shortened abstract

Recent advances in memory technologies are making it possible for machines with
    large amounts of memory to become commonplace.  Much research is currently
    being done to study how non-volatile and large memory systems would change
    system design.  We see the need for a lightweight tool to study such
    systems at scale with real workloads.  The first step towards building such
    a tool is to study the scalability of existing memory management systems.

We observe that in most cases, Linux kernel memory management scales well with
    large amounts of physical memory. However, we observe that some workloads
    can trigger poor behavior. In particular, workloads that allocated many
    virtual memory areas can accumulate significant memory and computational
    overhead of kernel metadata.

>>>>

Much research is currently being done to study how non-volatile and large memory
    systems would change system design.  We see the need for a lightweight tool
    to study such systems at scale with real workloads.  The first step towards
    building such a tool is to study the scalability of existing memory
    management systems.

We observe that in most cases, Linux kernel memory management scales well with
    large amounts of physical memory. However, workloads that allocated many
    virtual memory areas can accumulate significant memory and computational
    overhead of kernel metadata.
